Toronto Paramedic Services

### 2024-09-26 paper/paper.qmd
Needed to change shapefile for map so deleted shapefile folder + edited paper

To map this data, a shapefile with the boundaries for Toronto's FSAs was required. This data was acquired from the Open Government Data portal by the Government of Canada [@2021census]. Ambulance station location data was also considered in this analysis. This dataset provided by Toronto Paramedic Services [@torontoparamedicservices] and shared through the city of Toronto's Open Data portal [@opentorontodata], contains the exact geographic locations of each ambulance station within Toronto. Additional information about these datasets, including how they were prepared and used can be found in the Appendix (@sec-appendix).

@@

By examining EMS demand through different incident types, the investigation above finds that medical emergencies...

@@

library(maps)
library(sf)

@@

toronto_forward_sortation_areas <- st_read("~/Toronto_Paramedic_Services/data/TorontoForwardSortationAreas")
view(toronto_forward_sortation_areas)

@@

map_data <- read_csv(here::here("data/analysis_data/analysis_data_FOR_MAP.csv"))
#view(map_data)

@@

merged_map_data <- merge(toronto_forward_sortation_areas, map_data, by = "CFSAUID")
#view(merged_map_data)

@@

ggplot(merged_map_data) + 
  geom_sf(aes(fill = EMS_Demand_Driver)) +
  labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         x = "Longitude", y="Latitude", 
       caption = "Data Source: Open Canada 2021 Census & Toronto Paramedic Services") +
  theme_light() + theme(plot.title = element_text(hjust = 0.3)) +
  scale_fill_discrete(name = "EMS Demand Driver") +
  scale_fill_manual(values = c("lightblue"))

@@

The ambulance station location data was not modified for this analysis. It was mapped separately and added to @fig-map to create @(FIG NAME FOR SECOND MAP).

>>>>

To map this data, a shapefile with the boundaries for Toronto's FSAs was required. This data was acquired from the Open Government Data portal by the Government of Canada [@2021census]. Additional information about this dataset, including how it was prepared and used can be found in the Appendix (@sec-appendix).

@@

By examining EMS demand through different incident types, the investigation above finds that medical emergencies are responsible for a significantly large portion of 911 calls. However, this finding applies to the city of Toronto in general, and emergency calls for medical emergencies may not be the driver of EMS demand within individual regions of Toronto. Thus, the following part of this analysis looks to identify the driver for each Forward Sortation Area (FSA) in Toronto. If different FSAs have different drivers of EMS demand, then strategies that are tailored to each region's circumstance may be more effective in managing EMS demand across the city.

@fig-map

@@

library(maps)
library(sf)
library(repr)

@@

#toronto_forward_sortation_areas <- st_read("~/Toronto_Paramedic_Services/data/TorontoForwardSortationAreas")
#view(toronto_forward_sortation_areas)

@@

#map_data <- read_csv(here::here("data/analysis_data/analysis_data_FOR_MAP.csv"))
#view(map_data)

@@

#merged_map_data <- merge(toronto_forward_sortation_areas, map_data, by = "CFSAUID")
#view(merged_map_data)

@@

#options(repr.plot.width = 20, repr.plot.height = 16)

#ggplot(merged_map_data) + 
  #geom_sf(aes(fill = EMS_Demand_Driver)) +
  #labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         #x = "Longitude", y="Latitude", 
       #caption = "Data Source: Open Canada 2021 Census & Toronto Paramedic Services") +
  #theme_light() + theme(plot.title = element_text(hjust = 0.3)) +
  #scale_fill_discrete(name = "EMS Demand Driver") +
  #scale_fill_manual(values = c("lightblue")) +
  #geom_sf_label(mapping = aes(label = merged_map_data$CFSAUID), size = 3, check_overlap = TRUE)
```

@@
